---
title: "A meta-analysis for psychophysiological and emotional effects of video gaming"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
library(tidyverse)
library(googlesheets)
library(metamanager)
library(metafor)
library(metaviz)
# source("script/functions/get_from_gdrive.R")
source("script/functions/es_helpers.R")
# source("script/functions/verify_sheets.R")
source("script/add_age_groups.R")

wave2_path <- "Research/Video game psychophysiology meta/Data extraction/Wave 2/"
```


```{r, include=FALSE, cache= TRUE}
# Get and clean data
articles <- 
    get_from_gdrive(wave2_path, all_char = TRUE) %>% 
    # Drop empty rows
    mutate(sheet = map(sheet, ~drop_na(.x, id)))

game_table <- 
    gs_key("1JVUPh1YxAnCmF2LWhTo9Qb7thDO_WsSaq3PufYjw_90") %>% 
    gs_read(1)

cleaned <- 
    articles %>%    
    filter(file %in% c("Kristoffer_extract_2.csv", "Zoli_extract_2.csv", "Lydia_extract_2.csv", "Tamas_extract_2.csv", "Marcell_extract_2.csv")) %>% 
    unnest() %>% 
    # Keep only non-excluded files
    filter(is.na(exclude_reason)) %>% 
    add_age_groups() %>% 
    # Transform columns
    mutate_at(vars(year, context_length, measurement_n), funs(as.integer)) %>% 
    mutate_at(vars(`subsample_female%`, `subsample_non-caucasian%`, `subsample_overweigh%`, measurement_timing, measurement_mean, measurement_sd, measurement_corr, measurement_change_stat_value), funs(as.double)) %>% 
    mutate(during_game = if_else(measurement_timing < context_length, TRUE, FALSE, missing = NA))

```


```{r include=FALSE}
# Create datasets for easy counting
# Keep only one row per study
counting_article <-
    cleaned %>%     
    distinct(id, .keep_all = TRUE)

# Keep only one row per subsample
counting_subs <-
    cleaned %>%     
    distinct(id, subsample_id, .keep_all = TRUE)

# Keep all independent effect sizes
counting_es <-
    cleaned %>% 
    distinct(id, subsample_id, measurement_outcome, measurement_game, 
             .keep_all = TRUE)


games <-
    cleaned %>% 
    left_join(game_table, by = c("measurement_game" = "game_title")) %>% 
    select(id, year, measurement_game, starts_with("game")) %>% 
    # Replace NAs with 0s for dummy vars
    mutate_at(vars(game_adaptation:game_handheld), funs(if_else(is.na(.), 0L, .))) %>% 
    # Add game_violence based on ESRB content descriptors
    mutate(game_violence = str_detect(game_esrb_descriptors, "Violence"))

```

# Screening process
<!-- Data collection results -->
<!-- Screening results -->
<!-- Fulltext available results -->
<!-- Data available -->


# Exploratory data analysis
## Included studies
###Number of studies
```{r}
# Number of included articles
nrow(counting_article)
```
###Year of publication
```{r}
# Articles by year
count(counting_article, year)
# Plot
count(counting_article, year) %>% 
    ggplot() +
    aes(x = year, y = n, label = n) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 7)) +
    geom_point(size = 8, color = "red") +
    geom_linerange(aes(ymin = 0, ymax = n), color = "red") +
    geom_text(color = "white")
```

### Number of subsamples
```{r}
nrow(counting_subs)
```


###Type of publication
###Number of effect sizes
```{r}
nrow(counting_es)
```
###Type of effect size
```{r}
counting_subs %>% 
    count(study_design)

```

## Participants
###Aggregated sample size
```{r}
all_participants <- sum(counting_subs$measurement_n, na.rm = TRUE)
all_participants

counting_subs %>% 
    ggplot() +
    aes(x = measurement_n) +
    geom_histogram(bins = 30) +
    scale_x_log10()

```

###Age group of participants by subgroup
```{r}
counting_subs %>% 
    group_by(age_group) %>% 
    summarise(subsamples = n(),
              aggregated_n = sum(measurement_n, na.rm = TRUE)) %>% 
    arrange(-subsamples)
```

###Proportion of females,  non-caucasians, and overwheight participants by subsample (weighted)
```{r}
# Weighted sample stats 
counting_subs %>%
    select(id, subsample_id, `subsample_female%`:`subsample_overweigh%`, measurement_n) %>%
    set_names(str_replace(names(.), "subsample_(.*)%$", "\\1")) %>% 
    # Calculate weighted frequencies
    mutate_at(vars(female:overweigh), funs(`*`(., measurement_n))) %>% 
    # Calculate weighted proportions
    summarise_at(vars(female:overweigh),
                 funs(N = sum(., na.rm = TRUE), 
                      `%` = magrittr::divide_by(sum(., na.rm = TRUE), all_participants))) %>%
    gather(sample_property, value) %>% 
    separate(sample_property, c("sample", "property"), sep = "_") %>% 
    spread(property, value) %>% 
    mutate(`%` = `%` * 100)
```

## Games
###Number of included games

```{r}
cleaned %>% 
    filter(!duplicated(measurement_game)) %>% 
    nrow()
```

###Year of first publication
```{r}
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    count(game_year, sort = TRUE)

games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    group_by(game_year) %>% 
    count() %>% 
    ggplot() +
    aes(x = game_year, y = n, label = n) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 7)) +
    geom_col() +
    geom_text(nudge_y = .6) +
    coord_cartesian(ylim = c(0, 7)) +
    ggtitle("The year of game previews used in the studies")

games %>% 
    distinct(id, measurement_game, .keep_all = TRUE) %>% 
    transmute(measurement_game, year, game_year, gap_year = year - game_year) %>% 
    ggplot() +
    aes(x = year, y = gap_year, label = measurement_game) +
    geom_point() +
    ggrepel::geom_text_repel() +
    ggtitle("Difference between the study publication year and the game preview")

games %>% 
    distinct(id, measurement_game, .keep_all = TRUE) %>% 
    transmute(year, game_year, gap_year = year - game_year) %>% 
    summarise(mean = mean(gap_year, na.rm = TRUE))

# TODO: Create a plot that shows the number of games by year weighted by study number

library(wordcloud2)
cleaned %>% 
    distinct(id, measurement_game, .keep_all = TRUE) %>% 
    count(measurement_game, sort = TRUE) %>% 
    wordcloud2()
    

```


###Included genres
```{r}
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    separate_rows(game_genre, sep = "; ") %>% 
    group_by(game_genre) %>% 
    count(sort = TRUE)
```

###Included ESRB rating
```{r}
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    group_by(game_esrb_rating) %>% 
    count()
```

###Include ESRB content descriptors
```{r}
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    separate_rows(game_esrb_descriptors, sep = ", ") %>% 
    group_by(game_esrb_descriptors) %>% 
    count(sort = TRUE) %>% 
    print(n = 100)

games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    separate_rows(game_esrb_descriptors, sep = ", ") %>% 
    group_by(game_esrb_descriptors) %>% 
    count() %>% 
    ungroup() %>% 
    mutate(game_esrb_descriptors = factor(game_esrb_descriptors)) %>% 
    ggplot() +
        aes(y = n, x = fct_rev(game_esrb_descriptors), label = n) +
        geom_col() +
        scale_y_continuous(breaks = scales::pretty_breaks()) +
        labs(x = NULL, title = "ESRB content descriptors in the games", y = "Number of games") +
        geom_text(aes(y = 0.2)) +
        # Keep the NA-s in the plot to show how many games did not have cont descr
        coord_flip(ylim = c(0, 10))

# Content descriptors by game genres
# TODO: Check if data is correct. Looks strange
# TODO: Group by themes, e.g. Language and humor, Violance, Sex, Substance, Suggestive
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    separate_rows(game_esrb_descriptors, sep = ", ") %>% 
    separate_rows(game_genre, sep = "; ") %>% 
    count(game_genre, game_esrb_descriptors, sort = TRUE) %>% 
    mutate(game_esrb_descriptors = fct_rev(game_esrb_descriptors)) %>% 
    drop_na() %>% 
        ggplot() +
        aes(x = game_genre, y = game_esrb_descriptors, size = n) +
        geom_count() +
        scale_x_discrete(position = "top") +
        scale_size_continuous(breaks = round) +
        labs(y = "ESRB content descriptor", x = NULL, size = "Number of games") +
        theme(axis.text.x = element_text(angle = 30))
```

###Violent games vs. non-violent games
```{r}
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    mutate(game_violence = str_detect(game_esrb_descriptors, "Violence")) %>% 
    count(game_violence)
```

###Gaming modes (AR-VR / Exergames / Handheld games)
```{r}
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    gather(game_mode, value, game_exergame:game_handheld) %>% 
    mutate(game_mode = str_remove(game_mode, "game_")) %>% 
    group_by(game_mode) %>% 
    summarise(n = sum(value))
```

###Adapted games
```{r}
games %>% 
    distinct(measurement_game, .keep_all = TRUE) %>% 
    group_by(game_adaptation) %>% 
    count()
```

# Outcome measures
```{r}
# Categorization of outome measures
# Phsysiological measures
om_hr <- c("heart rate","pulse rate")
om_sym <- c("epinephrine","norepinephrine","left ventricular ejection time",
             "systolic blood pressure","diastolic blood pressure","mean arterial pressure",
             "skin conductance","Skin conductance", "eda positive change")
om_para <- c("high frequency hrv","rmssd")
om_horm <- c("cortisol","testosterone","dopamine")
om_other_phys <- c("pulse transit time","pulse pressure","diastolic function","stroke volume","cardiac index","heather index","mean systolic ejection rate","stroke volume index","total systemic resistance","vascular rigidity index","respiratory rate","cardiac contractility response","rate pressure product", "respiratory exchange ratio","qtc/qs2","low frequency hrv / high frequency hrv","low frequency hrv","very low frequency hrv","cardiac output","total peripheral resistance")
om_all_phys <- c(om_hr, om_sym, om_para, om_horm, om_other_phys)
om_temp_phys <- c(om_hr, om_sym, om_para)

# Psychological measures
om_stress <- c("anxiety","upset", "stress","tension")
om_joy <- c("happiness","enjoyment","pleasure")
om_eng <- c("involvement","flow","engagement")
om_arousal <- c("excitement","arousal","vigor")
om_anger <- c("anger","aggression","physical aggression","verbal aggression")
om_other_psy <- c("annoyance","embarrassment","frustration","sadness","negative affect","positive affect","liking","valence","dissatisfaction","relaxation","confusion","depression","fatigue")
om_all_psy <- c(om_stress, om_joy, om_eng, om_arousal, om_anger, om_other_psy)
om_temp_psy <- c(om_stress, om_joy)

aggregated_outcomes <- read_csv("data_extaction/supplementary_data/aggregated_outcomes.csv")
```


###Number of psychophysiological measures
```{r paged.print=TRUE}
# counting_es %>% 
#     distinct(id, measurement_outcome, .keep_all = TRUE) %>% 
#     filter(measurement_outcome %in% om_all_phys) %>% 
#     group_by(measurement_outcome) %>% 
#     summarise(subsamples = n(),
#               aggregated_n = sum(measurement_n, na.rm = TRUE)) %>% 
#     
#     arrange(-subsamples)

counting_es %>% 
    distinct(id,  measurement_game, measurement_outcome, .keep_all = TRUE) %>% 
    right_join(aggregated_outcomes, by = "measurement_outcome") %>% 
    filter(domain == "physiological") %>% 
    group_by(aggregated_outcome) %>% 
    summarise(subsamples = n(),
              aggregated_n = sum(measurement_n, na.rm = TRUE)) %>% 
    arrange(-subsamples)
```


###Number of subjective measures

```{r}
# counting_es %>% 
#     distinct(id, measurement_outcome, .keep_all = TRUE) %>% 
#     filter(measurement_outcome %in% om_all_psy) %>% 
#     group_by(measurement_outcome) %>% 
#     summarise(subsamples = n(),
#               aggregated_n = sum(measurement_n, na.rm = TRUE)) %>% 
#     arrange(-subsamples)

counting_es %>% 
    distinct(id, measurement_game, measurement_outcome, .keep_all = TRUE) %>% 
    right_join(aggregated_outcomes, by = "measurement_outcome") %>% 
    filter(domain == "psychological") %>% 
    group_by(aggregated_outcome) %>% 
    summarise(subsamples = n(),
              aggregated_n = sum(measurement_n, na.rm = TRUE)) %>% 
    arrange(-subsamples)
```

# Creating data table for analysis
```{r}
average_stats <-
    cleaned %>% 
    filter(!measurement_point == "change from baseline") %>% 
    select(id, study_design, measurement_outcome, measurement_point, measurement_mean, measurement_sd, measurement_corr) %>% 
    group_by(measurement_outcome) %>% 
    summarize(measurement_mean = mean(measurement_mean, na.rm = TRUE),
              measurement_sd = mean(measurement_sd, na.rm = TRUE),
              measurement_corr = mean(measurement_corr, na.rm = TRUE),
              n = n()) %>% 
    print(n = 50)

average_r <- 
    average_stats %>% 
    select(measurement_outcome,
           r = measurement_corr) %>% 
    drop_na(r)    


# Between subjects effects
between_effects <-
    cleaned %>% 
    filter(study_design == "between") %>% 
    group_by(file, id, subsample_id, measurement_game, measurement_outcome) %>% 
    arrange(measurement_point, .by_group = TRUE) %>% 
    mutate(bl_mean = first(measurement_mean),
           bl_sd = first(measurement_sd),
           bl_n = first(measurement_n)) %>% 
    slice(2:n()) %>% 
    ungroup %>% 
    mutate(d = mean2d_bw(m1 = bl_mean, 
                      m2 = measurement_mean, 
                      sd1 = bl_sd, 
                      sd2 = measurement_sd),
           g = d2g(d, measurement_n),
           g_var = gvar_bw(g = g, n1 = bl_n, n2 = measurement_n)
    )


# Within subject ES
within_effects <-
    cleaned %>% 
    filter(study_design == "within" & str_detect(measurement_point, "^\\d")) %>% 
    left_join(average_r, by = "measurement_outcome") %>% 
    group_by(file, id, subsample_id, measurement_game, measurement_outcome) %>% 
    arrange(measurement_point, .by_group = TRUE) %>% 
    mutate(bl_mean = first(measurement_mean),
           bl_sd = first(measurement_sd),
           bl_n = first(measurement_n)) %>% 
    slice(2:n()) %>%
    mutate(r = if_else(is.na(r), .5, r),
           d = mean2d(m1 = bl_mean, 
                      m2 = measurement_mean, 
                      sd1 = bl_sd, 
                      sd2 = measurement_sd, 
                      n1 = bl_n, 
                      n2 = measurement_n, r),
           g = d2g(d, measurement_n),
           g_var = gvar(g, measurement_n, r)
) %>% 
    ungroup()

# Between subject ES

# ES calculation for change statistics
change_effects <-
    cleaned %>% 
    filter(study_design == "within" & measurement_point == "change from baseline") %>%
    left_join(average_r, by = "measurement_outcome") %>% 
           # If there is no info about the correletion for a measure, use .5
    mutate(r = if_else(is.na(r), .5, r),
           # First fill the appropriate variables with the extracted values
           t = if_else(measurement_change_stat_type == "t", 
                       measurement_change_stat_value, NA_real_),
           d = if_else(measurement_change_stat_type == "d", 
                       measurement_change_stat_value, NA_real_),
           z = if_else(measurement_change_stat_type == "z", 
                       measurement_change_stat_value, NA_real_),
           p = if_else(measurement_change_stat_type == "p", 
                       measurement_change_stat_value, NA_real_),
           # Calculate d based on stats
           d = case_when(!is.na(p) ~ p2t(p = p, n = measurement_n),
                         !is.na(z) ~ z2d(z = z, n = measurement_n), 
                         !is.na(t) ~ t2d_rm(t = t, n = measurement_n, r = r), 
                         # Use the change means and sds to calculate d
                         is.na(measurement_change_stat_type) ~ 
                             mean2dz(md = measurement_mean, sdd = measurement_sd),
                         TRUE ~ d),
           # Calculate g 
            g = d2g(d = d, n = measurement_n),
            g_var = gvar(g = g, n = measurement_n, r = r))

all_effects <-
    bind_rows(change_effects,
          between_effects,
          within_effects) %>% 
    select(-starts_with("bl_")) %>% 
    left_join(game_table, by = c("measurement_game" = "game_title")) 
```

---------------

# Kristoffer's part

Calculating the effect sizes for each study and game. 
We set the baseline as Puzzle games
```{r message=FALSE, warning=FALSE}
all_effects %>% 
    separate_rows(game_genre, sep = "; ") %>%
    distinct(id, measurement_game, .keep_all = TRUE) %>% 
    count(game_genre)

hr_effects <-
    all_effects %>%
    filter(measurement_outcome %in% om_hr,
          !str_detect(authors, "Barry "), # This one seems wrong
           during_game == TRUE) %>%
    separate_rows(game_genre, sep = "; ") %>%
    rowwise() %>% 
    mutate(first_author = str_extract(authors, "([^\\s,]+)") %>% 
               str_glue(", {year}")
    ) %>% 
    group_by(first_author, year, id, measurement_game, game_genre) %>% 
    summarise(N = first(measurement_n),
              g = mean(g),
              g_var = mean(g_var),
              se = sqrt(g_var)/sqrt(N)) %>% 
    ungroup() %>%
    drop_na(game_genre) %>% 
    mutate(game_genre = fct_relevel(game_genre, "Puzzle"))
    
hr_rma <-
    rma.mv(yi = g, V = g_var, 
           mods = ~ game_genre, data = hr_effects)


hr_rma
```

## Cumulative forest plot
```{r fig.height=8}

viz_forest(hr_rma, 
           study_labels = hr_effects$first_author, 
           group = hr_effects$game_genre,
           variant = "thick",
           annotate_CI = TRUE,
           xlab = "Hedge's g (SE)", 
           x_limit = c(-0.5, 5),type = "cumulative"
            
            )

```

## Funnel plot
This shows a large publication bias, therefore the results should be regarded with caution.
```{r}
viz_funnel(rma.mv(yi = g, V = g_var, data = hr_effects),
           contours_col = "Greys",
           sig_contours = TRUE
           )
```


# Lydia's part
Calculating the effect sizes for each study and game. 
```{r message=FALSE, warning=FALSE}
violence_effects <-
    all_effects  %>% 
    filter(measurement_outcome %in% om_hr,
           !str_detect(authors, "Barry "), # Seems to be wrong
           game_exergame == 0,
           during_game == TRUE) %>%
    mutate(game_violence = str_detect(game_esrb_descriptors, "Violen") %>% 
                           if_else(is.na(.), FALSE, .)) %>% 
    rowwise() %>% 
    mutate(first_author = str_extract(authors, "([^\\s,]+)") %>% 
                          str_glue(", {year}")) %>% 
    group_by(first_author, year, id, measurement_game, game_violence) %>% 
    summarise(N = first(measurement_n),
              g = mean(g),
              g_var = mean(g_var),
              se = sqrt(g_var)/sqrt(N)) %>% 
    ungroup()

violence_effects %>% 
    count(measurement_game, game_violence, sort = TRUE) %>% 
    print(n = 100)

violence_effects %>% 
    count(game_violence)
    
violence_rma <-
    violence_effects %>% 
    rma.mv(yi = g, V = g_var, 
           mods = ~ game_violence, data = .)


```

# Forest plot
```{r fig.height=7}

viz_forest(violence_rma, 
           study_labels = violence_effects$first_author, 
           group = violence_effects$game_violence,
           # variant = "thick",
           annotate_CI = TRUE,
           xlab = "Hedge's g (SE)"
           
)

```

# Funnel plot
The funnel plot shows publication bias, therefore the resuls should be interpreted with caution.
```{r}
viz_funnel(rma.mv(yi = g, V = g_var, data = violence_effects),
           contours_col = "Greys",
           sig_contours = TRUE
)
```


###Outcome measures included in the analyses (more than 5 es-es)
###Number of measurement points (separately for phys and subjective measurements)

-----------------------------------------
# Calculating the effect sizes
## Number of studies with accurate 


-----------------------------------------

# Publication bias
## Funnel plots
## Egger tests
## Rank correlations
## Trim-and-fill

-----------------------------------------
# Main analysis - Overall effect on each outcome measure

## Physiological outcomes
### Effect of time

## Subjective outcomes
### Effect of time?

-----------------------------------------
# Moderation analyses
## Physiological outcomes
### Participant characteristics: age group, female%, non-caucasian%, overweight%, 
### Context: place, timing, game length, players, opponent, competition
### Game characteristics: year of game release, genre, adaptation, ESRB rating, ESRB content descriptors, violence, game modes

## Subjective outcomes
### Participant characteristics: age group, female%, non-caucasian%, overweight%, 
### Context: place, timing, game length, players, opponent, competition
### Game characteristics: year of game release, genre, adaptation, ESRB rating, ESRB content descriptors, violence, game modes

-----------------------------------------
# Sensitivity analyses
## Physiological outcomes
### Effect of study quality
### Effect of imprecise inference
### Effect of publication year, type of study, and study design
### Effect of outliers

## Subjective outcomes
### Effect of study quality
### Effect of imprecise inference
### Effect of publication year, type of study, and study design
### Effect of outliers


